Bathymetry is a measurement of submarine topography and can be used to understand shifts of the ocean floor and its depth. Knowledge of bathymetry is important for marine navigation, both civilian and military, as well as for monitoring the effects of storms on coastal environments. While direct measurement of bathymetry is possible, the process tends to be cost and time prohibitive. For example, amphibious vehicles are capable of spatially limited surveys of bathymetry in difficult surf-zone conditions but require significant resources to operate. As a result of these factors, surveys tend to be sparse in time. 


Current research focuses on a method to estimate bathymetry using surface measurements collected via remote sensing platforms, i.e. airborne, satellite, or onshore platforms. While bathymetry data is currently sparse due to observational limitations, the physics of waves are reasonably well understood. In particular, a dispersion relationship can be used to relate water depth to surface properties such as wave length and wave period. It is therefore possible to estimate bathymetry given observations of these parameters. Light Detection And Ranging (LiDAR) has been used to determine wave heights and Argus land-mounted video has been analyzed photogrammetrically to determine wave frequency and wave number. Both of these sources therefore provide valuable inputs for estimating coastal bathymetry in a more efficient manner than is currently available.


%GPS-equipped jet skis with fathometers use echo sounding to determine water depth,

Wave and bathymetric data has been collected in Duck, NC by the U.S. Army Corps of Engineers Coastal and Hydraulics Laboratory, including in situ measurements of bathymetry and measurements of the water surface. These measurements provide a method for testing algorithms to invert for bathymetry because the true bathymetry is available for comparison to the numerical estimates.

In Section 2 we discuss the forward model. We consider the problem in one dimension. This model describes the gradient of the wave energy flux is equal to the local mean rate of energy dissipation in a breaking wave. Together to this we discuss dispersion relationship to relate depth with some wave dynamics. Upwind method is used as a numerical scheme to solve the model. We derive the wave height from the model by providing the information about some wave properties, like wave number. To apply the wave number in our model we estimate the wave number beforehand to apply that in the wave height estimation. The numerical result part is represented with plots and analysis. These numerical results are also showing relations between different wave dynamics.    